Oregon average visit rates for saba & asthma emergency data set for metrapolitan per month

### 2018-06-04 r_scripts/analysis/oregon_asthma_er_saba_msa_count_results.Rmd
Updated gitignore to include jupyter notebook checkpoings.

@@

```{r}
ed_count <- summary_table_er %>% 
  rename(n_ed = n_visit) %>% 
  mutate(rate_per10k = (n_ed/POPESTIMATE2013)*10000,
         msa_name = gsub('(.*)-.*', '\\1', 
                      gsub('(.*)-.*', '\\1', gsub('(.*),.*','\\1',NAME))),
         month_name = factor(month.abb[month], 
            levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul",
                       "Aug", "Sep", "Oct", "Nov", "Dec")))
# saba counts
saba_count <- summary_table_pharmacy %>% 
  rename(n_saba = n_visit) %>% 
  mutate(rate_per1000 = (n_saba/POPESTIMATE2013)*1000,
         msa_name = gsub('(.*)-.*', '\\1', 
                      gsub('(.*)-.*', '\\1', gsub('(.*),.*','\\1',NAME))),
         month_name = factor(month.abb[month], 
            levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul",
                       "Aug", "Sep", "Oct", "Nov", "Dec")))
saba_count

>>>>

```{r message=FALSE, warning=FALSE, eval =F}

@@

```{r eval=F}
ed_count <- summary_table_er %>% 
  rename(n_ed = n_visit) %>% 
  mutate(rate_per10k = (n_ed/POPESTIMATE2013)*10000,
         msa_name = gsub('(.*)-.*', '\\1', 
                      gsub('(.*)-.*', '\\1', gsub('(.*),.*','\\1',NAME))),
         month_name = factor(month.abb[month], 
            levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul",
                       "Aug", "Sep", "Oct", "Nov", "Dec")))
# saba counts
saba_count <- summary_table_pharmacy %>% 
  rename(n_saba = n_visit) %>% 
  mutate(rate_per1000 = (n_saba/POPESTIMATE2013)*1000,
         msa_name = gsub('(.*)-.*', '\\1', 
                      gsub('(.*)-.*', '\\1', gsub('(.*),.*','\\1',NAME))),
         month_name = factor(month.abb[month], 
            levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul",
                       "Aug", "Sep", "Oct", "Nov", "Dec")))
saba_count
